Monte Carlo calculation to characterize neutron and gamma fields for ANITA neutron facility at TSL

### 2015-04-16 Paper2015.tex
Modified text of paper.
Introduced macro for U238.

In introduction, explained that we'll only present results for the 10.2cm collimator in the summary - other collimators in the final paper.

Added and tidied up todos.

Removed table about neutron yield - information to go in main text.

Completed text for the first part of the results section: neutron contour plot, neutron profile, neutron spectrum (with comparison to earlier results)

\usepackage{siunitx}
\DeclareSIUnit\photon{\ensuremath{\gamma}}
\DeclareSIUnit\proton{p}
\DeclareSIUnit\neutron{n}
\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfig}

\usepackage{todo}
% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

A detailed model of the ANITA geometry was implemented in Geant4.
This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
The spallation target is a tungsten cylinder of diameter \SI{0}{\cm} and length \SI{0}{\cm}.
The target is cooled by water and surrounded by a stainless-steel cooling jacket.
The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).

@@

Simulations were conducted using Geant4 version~TBD.
The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.
In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several locations.
In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre (check centre)~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.
The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

\begin{table}[!tbp]
\caption{Neutron yield under the umbra region at the standard user position}	%title of the table
	\label{table:NYieldRadiusEffectAtSUP}
	\centering
	\begin{tabular}{l c c c}
		\toprule
          {collimator}   		&{$< \SI{1}{\MeV}$}	&{$\geq 1 \& <\SI{10}{\MeV}$}	&{$\geq \SI{10}{\MeV}$}\\
          \cmidrule(r){2-4}
          {\si{\centi\metre}}	&						&{\SI{1e-6}{\neutron\per\cm\squared\per\proton}}	&\\
          \midrule
		3 		& 0.833 	& 0.975	& 0.525\\
		10.2 	& 1.394 	& 1.248	& 0.525\\
		30 		& 1.962 	& 1.555	& 0.650\\
           \bottomrule
	\end{tabular}
\end{table}

@@

In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
Part of the motivation for this work was to investigate whether improvements in the fidelity of the Geant4 model would lead to increased quantitative agreement.
Fig.~\ref{fig:SUPCollimator}

\begin{figure}
    \todo{}
    \caption{Neutron field at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
    \label{fig:SUPCollimator}
\end{figure}

\begin{figure}
    \todo{}
    \caption{Neutron profile at the Standard User Position downstream of the \SI{10.2}{\cm} collimator}
    \label{fig:SUPProfile}
\end{figure}

Fig.~\ref{fig:FirstComparison}\ldots

\begin{figure}
	\todo{Here we need figures showing the integral spectra on log-log plots and equilethargic spectra normalised to unit area above \SI{10}{\MeV}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:FirstComparison}
\end{figure}

>>>>

\usepackage{siunitx}
\DeclareSIUnit\photon{\ensuremath{\gamma}}
\DeclareSIUnit\proton{p}
\DeclareSIUnit\neutron{n}

\usepackage{booktabs}
\usepackage{graphicx}
\usepackage{epstopdf}
\usepackage{subfig}

\usepackage{todo}

\usepackage{bpchem}
\def\U238{\BPChem{\^{238}U}}

% correct bad hyphenation here
\hyphenation{op-tical net-works semi-conduc-tor}

@@

A detailed model of the ANITA geometry was implemented in Geant4.
This is illustrated in overview in Fig.~\ref{fig:ANITAoverview}
Description of the geometry is given in \cite{Prokofiev2009,Prokofiev14}; a summary only is given here.
The spallation target is a tungsten cylinder of diameter \SI{0}{\cm} and length \SI{0}{\cm}.
The target is cooled by water and surrounded by a stainless-steel cooling jacket.
The target assembly with its cooling jacket appears as a small blue rectangle in Fig.~\ref{fig:ANITAoverview}.
Lead shielding blocks in the target region are also modelled, and shown in red Fig.~\ref{fig:ANITAoverview}.
A large electromagnet surrounding the target is modelled and shown in Fig.~\ref{fig:ANITAoverview} in grey (iron) and yellow (copper).
An iron collimator with variable apertures is modelled  and shown downstream of the target (grey).
For brevity in this summary we only present results for the standard collimator size (\SI{10.2}{\cm} diameter); in the final paper we will present results for cylindrical collimators in the range from \SIrange{3}{30}{\cm} diameter.

@@

Simulations were conducted using Geant4 version~TBD.
The TBD intranuclear cascade model was selected in accordance with the results of earlier work~\cite{Platt13}, in which it performed well in simulations of neutron spallation in the region from \SIrange{0}{0}{\MeV}.\todo{Enter neutron energy range}
In the simulation protons were incident axially at an energy of \SI{180}{\MeV}.
Resulting gamma and neutron fields were evaluated at several locations.
In this paper results are presented for three of these: The Standard User Position (SUP), \SI{2.5}{\m} downstream of the target centre\todo{check centre}~\cite{Prokofiev2009}, the Close User Position (CUP), \SI{0}{\m} downstream of the target, and the CUP-TOF, \SI{0}{m} downstream of the target.\todo{Enter CUP \& CUP-TOF ranges}
The SUP, CUP and CUP-TOF positions are visible in blue in Fig.~\ref{fig:ANITAoverview}.
The SUP and CUP positions are of interest as they are positions used for SEE tests; the CUP-TOF position is the location of thin-film breakdown counter (TFBC) detectors used for beam monitoring and characterisation using time-of-flight (TOF) techniques.
Model validation will be demonstrated against CUP-TOF data (section~\ref{tbd}).

@@

In previous work Platt et al.~\cite{Platt13} reported simulations of a naked ANITA target, demonstrating good qualitative agreement with independent calculations and measurements of the fast neutron field at ANITA SUP~\cite{Prokofiev2009}.
Part of the motivation for this work was to investigate whether improvements in the fidelity of the geometry used in the Geant4 model would lead to increased quantitative agreement.
Fig.~\ref{fig:SUPCollimator} shows neutron fluence rate contours at the SUP position.
The collimation effect is clearly visible.
Fig.~\ref{fig:SUPProfile} compares simulated and measured neutron fluence profile at the SUP.
Measurements were taken with a TFBC in which \U238\ is the target material~\cite{Prokofiev2009}; accordingly, simulated results were folded in energy with the neutron fission cross section for \U238~\cite{tbd}.
The results show~\todo{Explain SUP profile results.}
The predicted neutron fluence rate above \SI{10}{\MeV} at a proton current of \SI{200}{\nA} is \SI{0}{\neutron\per\cm\squared\per\second}, compared to \SI{0}{\neutron\per\cm\squared\per\second} from earlier calculations~\cite{Platt13} and \SI{0}{\neutron\per\cm\squared\per\second} from the parameterisation~\cite{Prokofiev2009}.
The current calculations therefore underpredict the parameterisation by tbd\%.\todo{Quantify integral yield}

\begin{figure}[t]
    \todo{Show neutrons above \SI{10}{\MeV}}
    \caption{Neutron yield above \SI{10}{\MeV} at the Standard User Position.}
    \label{fig:SUPCollimator}
\end{figure}

\begin{figure}[t]
    \todo{Show SUP profile, compared to measurements}
    \caption{Neutron profile at the Standard User Position}
    \label{fig:SUPProfile}
\end{figure}

Fig.~\ref{fig:FirstComparison} compares calculated neutron yield versus energy in the umbra at the SUP with that predicted by the naked-target simulation~\cite{Platt13} and with the standard parameterisation of the ANITA sup spectrum~\cite{Prokofiev2009}.
The results show\ldots\todo{Discuss the results. Compare current with earlier calculations. Compare calculations with parameterisation.}

\begin{figure}[t]
	\subfloat[Integral fluence rate]{\hspace{\columnwidth}\todo{Integral spectra on log-log axes}}\\
	\subfloat[Equilethargic spectrum, normalised to fluence above \SI{10}{\MeV}]{\hspace{\columnwidth}\todo{Normalised spectra on lethargy axes}}
	\caption{Neuton spectrum at the SUP, showing comparison between the standard facility parameterisation~\cite{Prokofiev2009} and results from a naked Geant4 model~\cite{Platt13} and this work.}
	\label{fig:FirstComparison}
\end{figure}
